---
title: "EE video trial_China"
author: "Finley_Yu"
date: "2021/6/22"
output: html_document
---

```{r setup and load library}
# setup
set.seed(123)
library(tidyverse) # pipeline operation 
library(haven) 
library(ggplot2) # 
library(weights) # weighted result
library(srvyr) # deal with survey data
library(fastR2) 
library(readxl)
library(lavaan)
library(psych)
library(MBESS)
library(mediation)
library(here) # get current path
library(gtsummary)
library(reshape)
library(Rmisc)
```

```{r load dataset}
df_video_intervention_us <- readr::read_csv(here::here("us_data","us_video.csv"))

## variable coding ------
## SS: consent to participate
## QQ: grouping: 1 - intervention group a; 2 - intervention group b; 3 - intervention group c; 4 - control group
df_video_intervention$group <- as.factor(df_video_intervention$QQ)
## PartVQ: 1 - those who can see the fourth option; 2 - those who cannot
## LA (ordinary vaccine)\LB (COVID-19 vaccine): from 1 - strong disagree to 5 - strongly agree
## LC: 1 - yes; 2 - no
## Basic infomation Q1 - Q11
## 
df_video_intervention_us$age <- as.factor(df_video_intervention_us$Q3)
df_video_intervention_us$gender <- as.factor(df_video_intervention_us$Q4)
df_video_intervention_us$province <- as.factor(df_video_intervention_us$Q5)
df_video_intervention_us$ethnicity <- as.factor(df_video_intervention_us$Q6)
df_video_intervention_us$residence <- as.factor(df_video_intervention_us$Q7)
df_video_intervention_us$education <- as.factor(df_video_intervention_us$Q8)
df_video_intervention_us$occupation <- as.factor(df_video_intervention_us$Q9)
df_video_intervention_us$income <- as.factor(df_video_intervention_us$Q10)

```

## Sample characteristics(unchange)

```{r}
# Q1: Have you ever been diagnosed with the new coronavirus disease?
df_video_intervention %>% 
  group_by(QQ) %>% 
  summarise_at(vars(Q1, Q2_1, Q2_2, Q2_3, Q2_4, Q2_5), funs(counts))

# Q2: Has anyone in your family, neighbors, coworkers, friends or other people you know been diagnosed with the new coronavirus disease? (2-1: family member; 2-2: friend; 2-3 neighbors; 2-4 coworkers; 2-5 others)
df_video_intervention %>% 
  group_by(QQ) %>% 
  summarise_at(vars(Q1, Q2_1, Q2_2, Q2_3, Q2_4, Q2_5), funs(counts))

# Q3: Age
df_video_intervention %>% 
  group_by(QQ) %>% 
  summarise_at(vars(age), funs(counts))

# Q4: gender
df_video_intervention %>% 
  group_by(QQ) %>% 
  summarise_at(vars(gender), funs(counts))

# Q5: province
df_province <- df_video_intervention %>% 
  group_by(QQ) %>% 
  summarise_at(vars(province), funs(counts))
#write.csv(df_province, file = "result/tables/province.csv")

# Q6: ethnicity
df_video_intervention %>% 
  group_by(QQ) %>% 
  summarise_at(vars(ethnicity), funs(counts))

# Q7: residence
df_video_intervention %>% 
#  group_by(QQ) %>% 
  summarise_at(vars(residence), funs(counts))

# Q8: education
df_video_intervention %>% 
#  group_by(QQ) %>% 
  summarise_at(vars(education), funs(counts))

# Q9: occupation
df_video_intervention %>% 
  group_by(QQ) %>% 
  summarise_at(vars(occupation), funs(counts))

# Q10: income
df_video_intervention %>% 
  group_by(QQ) %>% 
  summarise_at(vars(income), funs(counts))

# Q11: Where do you receive your primary information on vaccine?
df_video_intervention %>% 
  group_by(QQ) %>% 
  summarise_at(vars(Q11_1, Q11_2, Q11_3, Q11_4, Q11_5, Q11_6, Q11_7), funs(counts))
```

There remains the doubt whether Q11 should be put into the sample characteristics section.

!!! All the statistical analysis (except for the counting) should be applied with sampling weights.

## Primary outcomes: vaccine hesitancy, hope, vaccination status

```{r}
### 1. vaccine hesitancy ---------
#### transform the negative problem scores to the positive 
attach(df_video_intervention_us)
df_video_intervention_us$vaccine_hesitancy <- ((6 - LA_1) + (6 - LA_2) + (6 - LA_3) + (6 - LA_4) + LA_5 +(6 - LA_6) + (6 - LA_7) + (6 - LA_8) + LA_9 + LA_10 + (6 - LA_11) + LA_12 + LA_13 + LA_14) / 14
df_video_intervention_us$vaccine_confidence <- 6 - df_video_intervention_us$vaccine_hesitancy
detach()

### 2. COVID-19 vaccine hesitancy ----
#### transform the negative problem scores to the positive 
attach(df_video_intervention_us)
df_video_intervention_us$covid19_vaccine_hesitancy <- ((6 - LB_1) + (6 - LB_2) + (6 - LB_3) + (6 - LB_4) + LB_5 +(6 - LB_6) + (6 - LB_7) + (6 - LB_8) + LB_9 + LB_10 + LB_11 + LB_12) / 12
df_video_intervention_us$covid19_vaccine_confidence <- 6 - df_video_intervention_us$covid19_vaccine_hesitancy
detach()

### 3. vaccination status ----
df_video_intervention_us$vaccination_status = ifelse(df_video_intervention_us$LC_2==2,0,1)

### 4. hope scale --------
# agency
df_video_intervention_us$agency = with(df_video_intervention_us, (I1_2 + I1_9 + I1_10 + I1_12)/4)
# pathway
df_video_intervention_us$pathway = with(df_video_intervention_us, (I1_1 + I1_4 + I1_6 + I1_8)/4)
# hope
df_video_intervention_us$hope = (df_video_intervention_us$agency + df_video_intervention_us$pathway)/2

### some statistics of outcome -----
df_video_intervention_us %>%
  group_by(vaccination_status) %>%
  summarise_at(vars(vaccine_hesitancy,  hope),
               list(~mean(.), ~sd(.), ~n()))

df_video_intervention_us %>%
  summarise_at(vars(vaccine_hesitancy,  hope),
               list(~mean(.), ~sd(.)))



summary(glm(data = df_video_intervention_us, vaccination_status~hope+vaccine_hesitancy, family = "binomial"))

summary(glm(data = df_video_intervention_us, hope~vaccine_hesitancy))


```

## Adding Weights

```{r}
#df_weight <- read_xlsx(path = "Weights.xlsx", sheet = 1, na = "NA")

#df_video_intervention$weight <- rep(0,12000)

#for (i in 1:12000){
 # j = df_video_intervention$Q4[i] # gender
 # k = df_video_intervention$Q5[i] # province
 # l = df_video_intervention$Q7[i] # residence
 # df_video_intervention$weight[i] = #as.numeric(df_weight[k,2*j+l-2]) 
#}
```

##Vaccine hesitancy ###Vaccine hesitancy (group by study arms)

```{r differences between the 4 study arms}
library(gtsummary)
df_video_intervention_us %>%
  filter(vaccination_status==0) %>%
  select(vaccine_hesitancy, QQ) %>%
  tbl_summary(
    statistic = all_continuous() ~ "{mean} ({sd})",
    by = QQ
  ) %>%
  add_p()

df_video_intervention_us %>%
  select(vaccination_status, QQ) %>%
  tbl_summary(
    statistic = all_continuous() ~ "{mean} ({sd})",
    by = QQ
  ) %>%
  add_p()  
```

###Common vaccine hesitancy

```{r visualization}
library(gtsummary)
df_video_intervention_us <- df_video_intervention_us %>%
  dplyr::mutate(
    income_level = case_when(
      as.numeric(income) <= 4 ~ 1,
      as.numeric(income) > 4 ~ 2),
    education_level = case_when(
      as.numeric(education) <= 3 ~ 1,
      as.numeric(education) > 3 ~ 2
    ), 
    age_level = case_when(
      as.numeric(age) <18 & as.numeric(age)<= 29 ~ 1,
       as.numeric(age) <30 & as.numeric(age)<= 39 ~ 2, 
      as.numeric(age) <40 & as.numeric(age)<= 49 ~ 3, 
      as.numeric(age) <50 & as.numeric(age)<= 59 ~ 4, 
      as.numeric(age) >=60 ~ 5
  ))
# grouped by intervention
library(ggplot2)
ggplot(data = df_video_intervention_us, mapping = aes(x = vaccine_hesitancy,  fill = as.factor(QQ))) + 
  geom_density(alpha = 0.3) + 
  labs(x = "Vaccine hesitancy", y = "Density", title = "")  + 
  theme(panel.background = element_rect())+ scale_fill_discrete(name = "Group", labels = c("Intervention group a", "Intervention group b", "Intervention group c", "Control group")) +
  theme(panel.grid=element_blank(),axis.line=element_line(size=0.5, colour="black"),panel.grid.minor = element_blank()) + # delete the the grid but save the axis
  theme_bw() # set background white

# grouped by age
library(ggplot2)
ggplot(data = df_video_intervention_us, mapping = aes(x = vaccine_hesitancy,  fill = as.factor(age_level))) + 
  geom_density(alpha = 0.3) + 
  labs(x = "Vaccine hesitancy", y = "Density", title = "")  + 
  theme(panel.background = element_rect())+ scale_fill_discrete(name = "Age group", labels = c("18 to 29", "30 to 39", "40 to 49", "50 to 59", "60 or above")) + theme(panel.grid=element_blank(),axis.line=element_line(size=0.5, colour="black"),panel.grid.minor = element_blank()) + # delete the the grid but save the axis
  theme_bw() # set background white

# grouped by gender
library(ggplot2)
ggplot(data = df_video_intervention_us, mapping = aes(x = vaccine_hesitancy,  fill = as.factor(gender))) + 
  geom_density(alpha = 0.3) + 
  labs(x = "Vaccine hesitancy", y = "Density", title = "")  + 
  theme(panel.background = element_rect())+ scale_fill_discrete(name = "Gender", labels = c("Male", "Female")) +
  theme(panel.grid=element_blank(),axis.line=element_line(size=0.5, colour="black"),panel.grid.minor = element_blank()) + # delete the the grid but save the axis
  theme_bw() # set background white

# grouped by residence
library(ggplot2)
ggplot(data = df_video_intervention_us, mapping = aes(x = vaccine_hesitancy,  fill = as.factor(residence))) + 
  geom_density(alpha = 0.3) + 
  labs(x = "Vaccine hesitancy", y = "Density", title = "")  + 
  theme(panel.background = element_rect())+ scale_fill_discrete(name = "Residence", labels = c("Rural", "Urban")) +
  theme(panel.grid=element_blank(),axis.line=element_line(size=0.5, colour="black"),panel.grid.minor = element_blank()) + # delete the the grid but save the axis
  theme_bw() # set background white


# grouped by education
library(ggplot2)
ggplot(data = df_video_intervention_us, mapping = aes(x = vaccine_hesitancy,  fill = as.factor(education))) + 
  geom_density(alpha = 0.3) + 
  labs(x = "Vaccine hesitancy", y = "Density", title = "")  + 
  theme(panel.background = element_rect())+ scale_fill_discrete(name = "Education", labels = c("No primary school", "Primary school", "Middle school", "High school", "College/undergraduate", "Master's degree","Doctorate")) +
  theme(panel.grid=element_blank(),axis.line=element_line(size=0.5, colour="black"),panel.grid.minor = element_blank()) + # delete the the grid but save the axis
  theme_bw() # set background white

# grouped by income
library(ggplot2)
ggplot(data = df_video_intervention_us, mapping = aes(x = covid19_vaccine_hesitancy,  fill = as.factor(income))) + 
  geom_density(alpha = 0.3) + 
  labs(x = "vaccine hesitancy", y = "Density", title = "")  + 
  theme(panel.background = element_rect())+ scale_fill_discrete(name = "Income", labels = c("<$10000", "$10000-29999", "$30000-49999", "$50000-69999", "$70000-89999", "$90000-109999", "$110000-129999", "$130000-149999", "$150000-199999", ">$200000")) +
  theme(panel.grid=element_blank(),axis.line=element_line(size=0.5, colour="black"),panel.grid.minor = element_blank()) + # delete the the grid but save the axis
  theme_bw() # set background white

# grouped by ethnicity
library(ggplot2)
ggplot(data = df_video_intervention_us, mapping = aes(x = covid19_vaccine_hesitancy,  fill = as.factor(ethnicity))) + 
  geom_density(alpha = 0.3) + 
  labs(x = "vaccine hesitancy", y = "Density", title = "")  + 
  theme(panel.background = element_rect())+ scale_fill_discrete(name = "ethnicity", labels = c("White", "Black or African American", "Asian or Asian American", "Mixed", "Other")) +
  theme(panel.grid=element_blank(),axis.line=element_line(size=0.5, colour="black"),panel.grid.minor = element_blank()) + # delete the the grid but save the axis
  theme_bw() # set background white



```

### COVID-19 vaccine hesitancy.

```{r}
# grouped by intervention
library(ggplot2)
ggplot(data = df_video_intervention_us, mapping = aes(x = covid19_vaccine_hesitancy,  fill = as.factor(QQ))) + 
  geom_density(alpha = 0.3) + 
  labs(x = "COVID-19 vaccine hesitancy", y = "Density", title = "")  + 
  theme(panel.background = element_rect())+ scale_fill_discrete(name = "Group", labels = c("Intervention group a", "Intervention group b", "Intervention group c", "Control group")) +
  theme(panel.grid=element_blank(),axis.line=element_line(size=0.5, colour="black"),panel.grid.minor = element_blank()) + # delete the the grid but save the axis
  theme_bw() # set background white

# grouped by age
library(ggplot2)
ggplot(data = df_video_intervention_us, mapping = aes(x = covid19_vaccine_hesitancy,  fill = as.factor(age_level))) + 
  geom_density(alpha = 0.3) + 
  labs(x = "COVID-19 vaccine hesitancy", y = "Density", title = "")  + 
  theme(panel.background = element_rect())+ scale_fill_discrete(name = "Age group", labels = c("18 to 29", "30 to 39", "40 to 49", "50 to 59", "60 or above")) + theme(panel.grid=element_blank(),axis.line=element_line(size=0.5, colour="black"),panel.grid.minor = element_blank()) + # delete the the grid but save the axis
  theme_bw() # set background white

# grouped by gender
library(ggplot2)
ggplot(data = df_video_intervention_us, mapping = aes(x = covid19_vaccine_hesitancy,  fill = as.factor(gender))) + 
  geom_density(alpha = 0.3) + 
  labs(x = "COVID-19 vaccine hesitancy", y = "Density", title = "")  + 
  theme(panel.background = element_rect())+ scale_fill_discrete(name = "Gender", labels = c("Male", "Female")) +
  theme(panel.grid=element_blank(),axis.line=element_line(size=0.5, colour="black"),panel.grid.minor = element_blank()) + # delete the the grid but save the axis
  theme_bw() # set background white

# grouped by residence
library(ggplot2)
ggplot(data = df_video_intervention_us, mapping = aes(x = covid19_vaccine_hesitancy,  fill = as.factor(residence))) + 
  geom_density(alpha = 0.3) + 
  labs(x = "COVID-19 vaccine hesitancy", y = "Density", title = "")  + 
  theme(panel.background = element_rect())+ scale_fill_discrete(name = "Residence", labels = c("Rural", "Urban")) +
  theme(panel.grid=element_blank(),axis.line=element_line(size=0.5, colour="black"),panel.grid.minor = element_blank()) + # delete the the grid but save the axis
  theme_bw() # set background white


# grouped by education
library(ggplot2)
ggplot(data = df_video_intervention_us, mapping = aes(x = covid19_vaccine_hesitancy,  fill = as.factor(education))) + 
  geom_density(alpha = 0.3) + 
  labs(x = "COVID-19 vaccine hesitancy", y = "Density", title = "")  + 
  theme(panel.background = element_rect())+ scale_fill_discrete(name = "Education", labels = c("No primary school", "Primary school", "Middle school", "High school", "College/undergraduate", "Master's degree","Doctorate")) +
  theme(panel.grid=element_blank(),axis.line=element_line(size=0.5, colour="black"),panel.grid.minor = element_blank()) + # delete the the grid but save the axis
  theme_bw() # set background white



# grouped by income
library(ggplot2)
ggplot(data = df_video_intervention_us, mapping = aes(x = covid19_vaccine_hesitancy,  fill = as.factor(income))) + 
  geom_density(alpha = 0.3) + 
  labs(x = "COVID-19 vaccine hesitancy", y = "Density", title = "")  + 
  theme(panel.background = element_rect())+ scale_fill_discrete(name = "Income", labels = c("<$10000", "$10000-29999", "$30000-49999", "$50000-69999", "$70000-89999", "$90000-109999", "$110000-129999", "$130000-149999", "$150000-199999", ">$200000")) +
  theme(panel.grid=element_blank(),axis.line=element_line(size=0.5, colour="black"),panel.grid.minor = element_blank()) + # delete the the grid but save the axis
  theme_bw() # set background white

# grouped by ethnicity
library(ggplot2)
ggplot(data = df_video_intervention_us, mapping = aes(x = covid19_vaccine_hesitancy,  fill = as.factor(ethnicity))) + 
  geom_density(alpha = 0.3) + 
  labs(x = "COVID-19 vaccine hesitancy", y = "Density", title = "")  + 
  theme(panel.background = element_rect())+ scale_fill_discrete(name = "ethnicity", labels = c("White", "Black or African American", "Asian or Asian American", "Mixed", "Other")) +
  theme(panel.grid=element_blank(),axis.line=element_line(size=0.5, colour="black"),panel.grid.minor = element_blank()) + # delete the the grid but save the axis
  theme_bw() # set background white

```

### T test of the vaccine hesitancy

Mean score and 95% CI of each treatment group.

```{r}
# t test
# treatment vs. control

df_video_intervention_a = subset(df_video_intervention,QQ==1)
df_video_intervention_b = subset(df_video_intervention,QQ==2)
df_video_intervention_c = subset(df_video_intervention,QQ==3)
df_video_intervention_control = subset(df_video_intervention,QQ==4)

wtd.t.test(df_video_intervention_a$vaccine_hesitancy_score, df_video_intervention_control$vaccine_hesitancy_score,df_video_intervention_a$weight,df_video_intervention_control$weight)

wtd.t.test(df_video_intervention_a$covid19_vaccine_hesitancy_score, df_video_intervention_control$covid19_vaccine_hesitancy_score,df_video_intervention_a$weight,df_video_intervention_control$weight)

wtd.t.test(df_video_intervention_b$vaccine_hesitancy_score, df_video_intervention_control$vaccine_hesitancy_score,df_video_intervention_b$weight,df_video_intervention_control$weight)

wtd.t.test(df_video_intervention_b$covid19_vaccine_hesitancy_score, df_video_intervention_control$covid19_vaccine_hesitancy_score,df_video_intervention_b$weight,df_video_intervention_control$weight)

wtd.t.test(df_video_intervention_c$vaccine_hesitancy_score, df_video_intervention_control$vaccine_hesitancy_score,df_video_intervention_c$weight,df_video_intervention_control$weight)

wtd.t.test(df_video_intervention_c$covid19_vaccine_hesitancy_score, df_video_intervention_control$covid19_vaccine_hesitancy_score,df_video_intervention_c$weight,df_video_intervention_control$weight)


#between treatments

df_vaccine_hesitancy_treatment = subset(df_video_intervention,QQ==1|QQ==2|QQ==3,select=c(QQ,vaccine_hesitancy_score,covid19_vaccine_hesitancy_score,weight))

ws=sum(df_vaccine_hesitancy_treatment$weight)

fit_vaccine=aov((vaccine_hesitancy_score*weight/ws) ~ factor(QQ), data=df_vaccine_hesitancy_treatment)

summary(fit_vaccine)

fit_covid19_vaccine=aov((covid19_vaccine_hesitancy_score*weight/ws) ~ factor(QQ), data=df_vaccine_hesitancy_treatment)

summary(fit_covid19_vaccine)

```

##Hope score(score, upper&lower value[each block])

```{r}
library(gtsummary)
df_video_intervention %>%
  mutate(
    income_level = case_when(
      as.numeric(income) <= 4 ~ 1,
      as.numeric(income) > 4 ~ 2),
    education_level = case_when(
      as.numeric(education) <= 3 ~ 1,
      as.numeric(education) > 3 ~ 2,
    )
  ) %>%
  select(income_level, education_level, residence, hope, vaccination_status) %>%
  summarise(
    hope_rural_yes = mean(hope[residence == 1 & vaccination_status == 1]),
    hope_rural_yes_n = sum(residence == 1 & vaccination_status == 1),
    hope_rural_yes_upp = mean(hope[residence == 1 & vaccination_status == 1]) + 1.96 * sd(hope[residence == 1 & vaccination_status == 1])/sqrt(hope_rural_yes_n),
    hope_rural_yes_low = mean(hope[residence == 1 & vaccination_status == 1]) - 1.96 * sd(hope[residence == 1 & vaccination_status == 1])/sqrt(hope_rural_yes_n),
    
    hope_rural_no = mean(hope[residence == 1 & vaccination_status == 0]),
    hope_rural_no_n = sum(residence == 1 & vaccination_status == 0),
    hope_rural_no_upp = mean(hope[residence == 1 & vaccination_status == 0]) + 1.96 * sd(hope[residence == 1 & vaccination_status == 0])/sqrt(hope_rural_no_n),
    hope_rural_no_low = mean(hope[residence == 1 & vaccination_status == 0]) - 1.96 * sd(hope[residence == 1 & vaccination_status == 0])/sqrt(hope_rural_no_n),
    
    hope_poor_yes = mean(hope[income_level == 1 & vaccination_status == 1]),
    hope_poor_yes_n = sum(income_level == 1 & vaccination_status == 1),
    hope_poor_yes_upp = mean(hope[income_level == 1 & vaccination_status == 1]) + 1.96 * sd(hope[income_level == 1 & vaccination_status == 1])/sqrt(hope_poor_yes_n),
    hope_poor_yes_low = mean(hope[income_level == 1 & vaccination_status == 1]) - 1.96 * sd(hope[income_level == 1 & vaccination_status == 1])/sqrt(hope_poor_yes_n),
    
    hope_poor_no = mean(hope[income_level == 1 & vaccination_status == 0]),
    hope_poor_no_n = sum(income_level == 1 & vaccination_status == 0),
    hope_poor_no_upp = hope_poor_no + 1.96 * sd(hope[income_level == 1 & vaccination_status == 0])/sqrt(hope_rural_yes_n),
    hope_poor_no_low = hope_poor_no - 1.96 * sd(hope[income_level == 1 & vaccination_status == 0])/sqrt(hope_rural_yes_n),
    
    hope_lowedu_yes = mean(hope[education_level == 1 & vaccination_status == 1]),
    hope_lowedu_yes_n = sum(education_level == 1 & vaccination_status == 1),
    hope_lowedu_yes_upp = hope_lowedu_yes + 1.96 * sd(hope[education_level == 1 & vaccination_status == 1])/sqrt(hope_lowedu_yes_n),
    hope_lowedu_yes_low = hope_lowedu_yes - 1.96 * sd(hope[education_level == 1 & vaccination_status == 1])/sqrt(hope_lowedu_yes_n),
    
    hope_lowedu_no = mean(hope[education_level == 1 & vaccination_status == 0]),
    hope_lowedu_no_n = sum(education_level == 1 & vaccination_status == 0),
    hope_lowedu_no_upp = hope_lowedu_no + 1.96 * sd(hope[education_level == 1 & vaccination_status == 0])/sqrt(hope_lowedu_no_n),
    hope_lowedu_no_low = hope_lowedu_no - 1.96 * sd(hope[education_level == 1 & vaccination_status == 0])/sqrt(hope_lowedu_no_n),
  )
```

###Mediation analysis

```{r mediation analysis}
sink("mediation regression.txt")
hope_tibble<-df_video_intervention %>% 
#  group_by(vaccination_status) %>%
  summarise(mean(hope)) 
hope_tibble
confidence_tibble<-df_video_intervention %>%
#  group_by(vaccination_status) %>%
  summarise(mean(vaccine_confidence))
confidence_tibble

summary(glm(data = df_video_intervention, vaccination_status ~ hope, family = binomial())) 
summary(lm(data = df_video_intervention, vaccination_status ~ hope + vaccine_confidence, famil = binomial()))

sink()

mod1 <- "# a path
         vaccine_confidence ~ a * hope

         # b path
         vaccination_status ~ b * vaccine_confidence

         # c prime path 
         vaccination_status ~ cp * hope

         # indirect and total effects
         ab := a * b
         total := cp + ab"

fsem1 <- sem(mod1, data = df_video_intervention, se = "bootstrap", bootstrap = 10000) # fit structural equation models

sink("fsem.txt")
summary(fsem1)
sink()

model1 <- lm(data = df_video_intervention, vaccine_confidence ~ hope + age + gender 
             + residence + education + occupation + income)
model2 <- glm(data = df_video_intervention, vaccination_status ~ hope + vaccine_confidence + age + gender + residence + education + occupation + income, family = "binomial")
sem <- mediate(model1, model2, treat = "hope", mediator = "vaccine_confidence", boot = T)

sink("sem.txt")
summary(sem)
plot(sem)
sink()

model1 <- lm(data = df_video_intervention, vaccine_confidence ~ hope)
model2 <- glm(data = df_video_intervention, vaccination_status ~ hope + vaccine_confidence, family = "binomial")
sem0 <- mediate(model1, model2, treat = "hope", mediator = "vaccine_confidence", boot = T)

summary(sem0)
plot(sem0)


# semb<-mediate(vaccination_status ~ hope +  (vaccine_hesitancy), z = age + male + urban  + college + poor + provider, data = comdem[black == 1,], n.iter = 10000)
# sink("fsem_blk.txt")
# summary(semb)
# 
# sink()
# 
# 
# semu<-mediate(vaccination_status ~ hope +  (vaccine_hesitancy), z = age + male  + black + college + poor + provider, data = comdem[urban == 1,], n.iter = 10000)
# sink("fsem_urban.txt")
# 
# summary(semu)
# sink()
# 
# semu<-mediate(vaccination_status ~ hope +  (vaccine_hesitancy), z = age + male  + black + college + poor + provider, data = comdem[urban == 0,], n.iter = 10000)
# semc<-mediate(vaccination_status ~ hope +  (vaccine_hesitancy), z = age + male  + black + urban + poor + provider, data = comdem[college == 0,], n.iter = 10000)
# semp<-mediate(vaccination_status ~ hope +  (vaccine_hesitancy), z = age + male  + black + urban + college + provider, data = comdem[poor == 1,], n.iter = 10000)
# 
# sink("fsem_ucp.txt")
# 
# summary(semu)
# summary(semc)
# summary(semp)
# sink()
# 
# semm<-mediate(vaccination_status ~ hope +  (vaccine_hesitancy), z = age + male + urban + black + college + poor + provider, data = comdem, n.iter = 10000)

```

```{r}
# write table ----
#setwd("C:/Users/Finley/Desktop/research/healthcare/task 7 trial/")

#write.csv(df_vaccine_hesitancy,file = "result/tables/vaccine hesitancy.csv")
#write.csv(df_covid19_vaccine_hesitancy,file = "result/tables/covid19 vaccine hesitancy.csv")
```

## list experiment

Using the data in the list experiment

Maybe you need to do the double-check with the list experiment analysis approaches in the related literature.

```{r}
df_list_baseline = df_video_intervention[df_video_intervention$PartVQ == 2, ]
df_list_treatment = df_video_intervention[df_video_intervention$PartVQ == 1, ]

# baseline
#result1<- df_list_baseline %>%
  #summarise_at(vars(PartVA_5_T, PartVB_5_T, PartVC_5_T, PartVD_5_T), funs(mean = wtd.mean(.,weight), sd = sqrt(wtd.var(.,weight))/sqrt(length(.))))
result1 <- df_list_baseline %>%
  summarise_at(vars(PartVA_5_T, PartVB_5_T, PartVC_5_T, PartVD_5_T),
               funs(mean(.)))
result1 <- result1 %>%
  dplyr::mutate( total = PartVA_5_T + PartVB_5_T + PartVC_5_T + PartVD_5_T)
result1 <- t(result1)
result1 <- as.data.frame(result1)
names(result1) <- c("baseline")

# treatment
#result2 <- df_list_treatment %>%
  #summarise_at(vars(PartVA_5_T, PartVB_5_T, PartVC_5_T, PartVD_5_T), funs(mean = wtd.mean(.,weight), sd = sqrt(wtd.var(.,weight))/sqrt(length(.))))
#result2
result2 <- df_list_treatment %>%
  summarise_at(vars(PartVA_5_T, PartVB_5_T, PartVC_5_T, PartVD_5_T),
               funs(mean(.)))
result2 <- result2 %>%
  mutate(total=PartVA_5_T+PartVB_5_T+PartVC_5_T+PartVD_5_T)
result2 <- t(result2)
result2 <- as.data.frame(result2)
names(result2) <- c("treatment")
#table for list outcome
df_list_outcome <- result1
df_list_outcome <- df_list_outcome %>%
  mutate(result2) %>%
  mutate(difference = treatment - baseline)

# difference in means??weighted)
bs = sum(df_list_baseline$weight)
ts = sum(df_list_treatment$weight)
cbind(((bs*result2-ts*result1)/(bs+ts))[1:4],sqrt((bs*result1^2 + ts*result2^2)/(bs+ts))[5:8])

#t test for list experiment


```

### referece code

```{r}
#df_list_baseline %>% 
 # summarise_at(vars(PartVA_5_T, PartVB_5_T, PartVC_5_T, PartVD_5_T), funs(counts(.)))

#df_list_treatment %>% 
#  summarise_at(vars(PartVA_5_T, PartVB_5_T, PartVC_5_T, PartVD_5_T), funs(counts(.)))

# baseline
#df_control_baseline = subset(df_list_baseline,QQ == 4,select = c(PartVA_5_T, PartVB_5_T, PartVC_5_T, PartVD_5_T,weight))
#df_intervention_baseline = subset(df_list_baseline,QQ != 4, select = c(PartVA_5_T, PartVB_5_T, PartVC_5_T, PartVD_5_T,weight))

#wtd.t.test(df_control_baseline$PartVA_5_T,df_intervention_baseline$PartVA_5_T,df_control_baseline$weight,df_intervention_baseline$weight)
#wtd.t.test(df_control_baseline$PartVB_5_T,df_intervention_baseline$PartVB_5_T,df_control_baseline$weight,df_intervention_baseline$weight)
#wtd.t.test(df_control_baseline$PartVC_5_T,df_intervention_baseline$PartVC_5_T,df_control_baseline$weight,df_intervention_baseline$weight)
#wtd.t.test(df_control_baseline$PartVD_5_T,df_intervention_baseline$PartVD_5_T,df_control_baseline$weight,df_intervention_baseline$weight)

# intervention
#df_control_treatment = subset(df_list_treatment,QQ == 4,select = c(PartVA_5_T, PartVB_5_T, PartVC_5_T, PartVD_5_T,weight))
#df_intervention_treatment = subset(df_list_treatment,QQ != 4, select = c(PartVA_5_T, PartVB_5_T, PartVC_5_T, PartVD_5_T,weight))

#wtd.t.test(df_control_treatment$PartVA_5_T,df_intervention_treatment$PartVA_5_T,df_control_treatment$weight,df_intervention_treatment$weight)
#wtd.t.test(df_control_treatment$PartVB_5_T,df_intervention_treatment$PartVB_5_T,df_control_treatment$weight,df_intervention_treatment$weight)
#wtd.t.test(df_control_treatment$PartVC_5_T,df_intervention_treatment$PartVC_5_T,df_control_treatment$weight,df_intervention_treatment$weight)
#wtd.t.test(df_control_treatment$PartVD_5_T,df_intervention_treatment$PartVD_5_T,df_control_treatment$weight,df_intervention_treatment$weight)
```

##Engagement

```{r}
#
df_video_intervention <- df_video_intervention%>%
  tidyr::replace_na(list(TA2_2_T=0, TB2_2_T=0, TC2_2_T=0))
df_video_intervention <- df_video_intervention %>%
  mutate (watching_time_1 = TA2_2_T + TB2_2_T+ TC2_2_T)
df_watchingtime <-  df_video_intervention$watching_time_1
s <- tibble(s = 1:12000)
df_watchingtime <- sort(df_watchingtime)
df_watchingtime <- as.data.frame(df_watchingtime)
df_watchingtime <- df_watchingtime %>%
  srvyr::mutate(s)

#s <- tibble(s = 1:12000)
#df_watchingtime <- sort(df_watchingtime$df_watchingtime)
#df_watchingtime <- as.data.frame(df_watchingtime)
#df_watchingtime <- df_watchingtime %>%
#  srvyr::mutate(s)
#25%50%75% (average time)
df_watchingtime <- df_watchingtime %>%
  srvyr::mutate(
    group = dplyr::case_when(
      as.numeric(s) <= 3000 ~ 1,
      as.numeric(s) > 3000 & as.numeric(s)<= 6000 ~ 2, 
      as.numeric(s) > 6000 & as.numeric(s)<= 9000 ~ 3,
      as.numeric(s) > 9000 ~ 4 )
  )
mutate
 t <- df_watchingtime %>%
  group_by(group)%>%
  summarise_at(vars(df_watchingtime),list(~mean(.)))
#videoA
 df_watchingtime_A <-  df_video_intervention$TA2_2_T
 df_watchingtime_A <- as.data.frame(df_watchingtime_A)
 df_watchingtime_A <- df_watchingtime_A %>%
  dplyr::mutate(
    N = dplyr::case_when(
      as.numeric(df_watchingtime_A) <= 0 ~ 0,
      as.numeric(df_watchingtime_A) > 0 ~ 1 )
  ) 
cA <- df_watchingtime_A %>%
  summarise_at(vars(N), funs(counts))
  df_watchingtime_A <- sort(df_watchingtime_A$df_watchingtime_A)
   df_watchingtime_A <- as.data.frame(df_watchingtime_A)
df_watchingtime_A <- df_watchingtime_A %>%
  dplyr::mutate(s)
df_watchingtime_A <- df_watchingtime_A %>%
  mutate(
    group = case_when(
      as.numeric(s) <= 8072 ~ 1,
      as.numeric(s) > 8072 & as.numeric(s)<= 9054 ~ 2, 
      as.numeric(s) > 9054 & as.numeric(s)<= 10036 ~ 3,
      as.numeric(s) > 10036 & as.numeric(s)<= 11018 ~ 4,
     as.numeric(s) > 11018 ~ 5 )
  ) 

 tA <- df_watchingtime_A %>%
  group_by(group)%>%
  summarise_at(vars(df_watchingtime_A),list(~mean(.)))
 
 #videoB
 
  df_watchingtime_B <-  df_video_intervention$TB2_2_T
 df_watchingtime_B <- as.data.frame(df_watchingtime_B)
 df_watchingtime_B <- df_watchingtime_B %>%
  dplyr::mutate(
    N = dplyr::case_when(
      as.numeric(df_watchingtime_B) <= 0 ~ 0,
      as.numeric(df_watchingtime_B) > 0 ~ 1 )
  ) 
cB <- df_watchingtime_B %>%
  summarise_at(vars(N), funs(counts))
  df_watchingtime_B <- sort(df_watchingtime_B$df_watchingtime_B)
   df_watchingtime_B <- as.data.frame(df_watchingtime_B)
df_watchingtime_B <- df_watchingtime_B %>%
  dplyr::mutate(s)
df_watchingtime_B <- df_watchingtime_B %>%
  mutate(
    group = case_when(
      as.numeric(s) <= 8451 ~ 1,
      as.numeric(s) > 8451 & as.numeric(s)<= 9338 ~ 2, 
      as.numeric(s) > 9338 & as.numeric(s)<= 10225 ~ 3,
      as.numeric(s) > 10225 & as.numeric(s)<= 11112 ~ 4,
     as.numeric(s) > 11112 ~ 5 )
  ) 

 tB <- df_watchingtime_B %>%
  group_by(group)%>%
  summarise_at(vars(df_watchingtime_B),list(~mean(.)))
 #videoC
   df_watchingtime_C <-  df_video_intervention$TC2_2_T
 df_watchingtime_C <- as.data.frame(df_watchingtime_C)
 df_watchingtime_C <- df_watchingtime_C %>%
  dplyr::mutate(
    N = dplyr::case_when(
      as.numeric(df_watchingtime_C) <= 0 ~ 0,
      as.numeric(df_watchingtime_C) > 0 ~ 1 )
  ) 
cC <- df_watchingtime_C %>%
  summarise_at(vars(N), funs(counts))
  df_watchingtime_C <- sort(df_watchingtime_C$df_watchingtime_C)
   df_watchingtime_C <- as.data.frame(df_watchingtime_C)
df_watchingtime_C <- df_watchingtime_C %>%
  dplyr::mutate(s)
df_watchingtime_C <- df_watchingtime_C %>%
  mutate(
    group = case_when(
      as.numeric(s) <= 8485 ~ 1,
      as.numeric(s) > 8485 & as.numeric(s)<= 9363 ~ 2, 
      as.numeric(s) > 9363 & as.numeric(s)<= 10241 ~ 3,
      as.numeric(s) > 10241 & as.numeric(s)<= 11119 ~ 4,
     as.numeric(s) > 11119 ~ 5 )
  ) 

 tC <- df_watchingtime_C %>%
  group_by(group)%>%
  summarise_at(vars(df_watchingtime_C),list(~mean(.)))
#yes or no page
 
 df_engagement_yon <- df_video_intervention%>%
   subset.data.frame(select = QQ1_4)
 c_yon <- df_engagement_yon %>%
  summarise_at(vars(QQ1_4), funs(counts))%>%
   mutate(p = QQ1_4/12000)
 #what is their true choice(less than 30% & more than 70%)
 df_engagement_true <- df_video_intervention %>%
   subset.data.frame(select = c(TA2_2_T,TB2_2_T,TC2_2_T))%>%
   mutate(va = case_when(TA2_2_T<=23700 ~ 0,
                         TA2_2_T> 23700 & TA2_2_T<= 55300 ~ 1,
                         TA2_2_T>55300 ~2))%>%
   mutate(vb = case_when(TB2_2_T<=25200 ~ 0,
                         TB2_2_T> 25200 & TB2_2_T<= 58800 ~ 1,
                         TB2_2_T>58800 ~2))%>%
   mutate(vc = case_when(TC2_2_T<=54600 ~ 0,
                         TC2_2_T> 54600 & TC2_2_T<= 12740 ~ 1,
                         TC2_2_T>12740 ~2))
 ##counting
  c_ture <- df_engagement_true %>%
  summarise_at(vars(c(va,vb)), funs(counts))%>% 
    mutate( level = 0:2)
  c_ture_vc <-  df_engagement_true %>%
  summarise_at(vars(c(vc)), funs(counts))%>% 
    mutate( level = c(0,2))
  c_ture <- left_join(c_ture,c_ture_vc,by ="level" )
  ##
  df_engagement_ture_n <- df_engagement_true %>%
     summarise(
       va_vb_n = sum(va == 0 & vb == 2),
     va_vc_n = sum(va == 0 & vc == 2),
     vb_va_n = sum(vb == 0 & va == 2),
     vb_vc_n = sum(vb == 0 & vc == 2),
     vc_va_n = sum(vc == 0 & va == 2),
     vc_vb_n = sum(vc == 0 & vb == 2)
     )
 ##confidence interval (99%, 95%, 75%)
  x <- df_watchingtime$df_watchingtime
  CI(x,ci = 0.95)
  CI(x,ci = 0.99)
  CI(x,ci = 0.50)
  x <- df_watchingtime_A$df_watchingtime_A
  CI(x,ci = 0.95)
  CI(x,ci = 0.99)
  CI(x,ci = 0.50)
  x <- df_watchingtime_B$df_watchingtime_B
  CI(x,ci = 0.95)
  CI(x,ci = 0.99)
  CI(x,ci = 0.50)
  x <- df_watchingtime_C$df_watchingtime_C
  CI(x,ci = 0.95)
  CI(x,ci = 0.99)
  CI(x,ci = 0.50)
  ##Geom_violin
  #table
  df_watchingtime_violin <-  df_video_intervention%>% 
select(watching_time_1, TA2_2_T, TB2_2_T, TC2_2_T)%>%
dplyr::rename(videoA=TA2_2_T)%>%
dplyr::rename(videoB=TB2_2_T)%>%
dplyr::rename(videoC=TC2_2_T)%>%
dplyr::rename(Total=watching_time_1)%>%    
    pivot_longer(cols = 'Total':'videoC',
                 names_to = "group",
                 values_to = "watching_time")
  

  watching_sina<- df_watchingtime_violin%>%
  ggplot(aes(x = group, y = watching_time)) +
  geom_violin(color = "transparent", fill = "gray90") +
  geom_jitter(width = 0.25, size = 0.85) +
  xlab("Group") +
  ylab("Watching time(ms)") +
  theme_classic(base_size = 14) +
  theme(
    axis.text = element_text(
      color = "black",
      size = 12
    ),
    plot.margin = margin(3, 7, 3, 1.5)
  )+
geom_hline(aes(yintercept = 70000),
                colour="blue",
                linetype="dashed",
                size=1)+
geom_hline(aes(yintercept = 90000),
                colour="blue",
                linetype="dashed",
                size=1)+
geom_hline(aes(yintercept = 180000),
                colour="blue",
                linetype="dashed",
                size=1)+
geom_hline(aes(yintercept = 270000),
                colour="blue",
                linetype="dashed",
                size=1)+
geom_hline(aes(yintercept = 350000),
                colour="blue",
                linetype="dashed",
                size=1)
watching_sina

  
  plot1 <- ggplot(df_watchingtime,aes(df_watchingtime))+
    theme_minimal(base_size = 9)+
    geom_density(aes(colour = Species,fill = Species),alpha = 0.5)+
    labs(title = "Density 密度曲线")+
    theme(plot.title = element_text(hjust = 0.5),
        legend.position = c(0.8,0.8))
  plot1
```

```{r}
# between age

sum_of_weight = sum(df_video_intervention$weight)

df_vaccine_hesitancy_age = subset(df_video_intervention,select=c(age,vaccine_hesitancy_score,covid19_vaccine_hesitancy_score,weight))

fit_vaccine_age=aov(vaccine_hesitancy_score*weight/sum_of_weight ~ factor(age), data=df_vaccine_hesitancy_age)

summary(fit_vaccine_age)

fit_covid19_vaccine_age=aov(covid19_vaccine_hesitancy_score*weight/sum_of_weight ~ factor(age), data=df_vaccine_hesitancy_age)

summary(fit_covid19_vaccine_age)

# Gender

df_vaccine_hesitancy_male = subset(df_video_intervention,gender ==1,select=c(vaccine_hesitancy_score,covid19_vaccine_hesitancy_score,weight))
df_vaccine_hesitancy_female = subset(df_video_intervention,gender ==2,select=c(vaccine_hesitancy_score,covid19_vaccine_hesitancy_score,weight))
wtd.t.test(df_vaccine_hesitancy_male$vaccine_hesitancy_score,df_vaccine_hesitancy_female$vaccine_hesitancy_score,df_vaccine_hesitancy_male$weight,df_vaccine_hesitancy_female$weight)
wtd.t.test(df_vaccine_hesitancy_male$covid19_vaccine_hesitancy_score,df_vaccine_hesitancy_female$covid19_vaccine_hesitancy_score,df_vaccine_hesitancy_male$weight,df_vaccine_hesitancy_female$weight)

# Residence

df_vaccine_hesitancy_rural = subset(df_video_intervention,residence ==1,select=c(vaccine_hesitancy_score,covid19_vaccine_hesitancy_score,weight))
df_vaccine_hesitancy_urban = subset(df_video_intervention,residence ==2,select=c(vaccine_hesitancy_score,covid19_vaccine_hesitancy_score,weight))
wtd.t.test(df_vaccine_hesitancy_rural$vaccine_hesitancy_score,df_vaccine_hesitancy_urban$vaccine_hesitancy_score,df_vaccine_hesitancy_rural$weight,df_vaccine_hesitancy_urban$weight)
wtd.t.test(df_vaccine_hesitancy_rural$covid19_vaccine_hesitancy_score,df_vaccine_hesitancy_urban$covid19_vaccine_hesitancy_score,df_vaccine_hesitancy_rural$weight,df_vaccine_hesitancy_urban$weight)

# Education

df_vaccine_hesitancy_education = subset(df_video_intervention,select=c(education,vaccine_hesitancy_score,covid19_vaccine_hesitancy_score,weight))

fit_vaccine_education=aov(vaccine_hesitancy_score*weight/sum_of_weight ~ factor(education), data=df_vaccine_hesitancy_education)

summary(fit_vaccine_education)

fit_covid19_vaccine_education=aov(covid19_vaccine_hesitancy_score*weight/sum_of_weight ~ factor(education), data=df_vaccine_hesitancy_education)

summary(fit_covid19_vaccine_education)
```

## Visualization of the vaccine hesitancy

Mean score and 95% CI of each treatment group.

```{r}
# Visualization

library(ggplot2)
library(ggpubr)
my_comparisons = list(c("3","4"),c("2","4"),c("1","4"))

ggplot(data = df_video_intervention, mapping = aes(x = QQ,y=wtd.mean(vaccine_hesitancy_score,weight),ymin=wtd.mean(vaccine_hesitancy_score,weight)-sqrt(wtd.var(vaccine_hesitancy_score,weight))*1.96,ymax=wtd.mean(vaccine_hesitancy_score,weight)+sqrt(wtd.var(vaccine_hesitancy_score,weight))*1.96,color=QQ)) + 
  geom_point(size=3) + 
  geom_errorbar(size=1,width=0.2) +
  stat_compare_means(comparisons=my_comparisons) +
  labs(x = "Intercention Group", y = "vaccine_hesitancy_score", title = "") +
  theme(panel.grid=element_blank(),axis.line=element_line(size=0.5, colour="black"),panel.grid.minor = element_blank()) + 
  theme_bw()

```

## Regression and maps

Model 1: Vaccine hesitancy \~ treatment + province

Visualization: Draw the coefficient of province on the China map.

Model 2: Vaccine hesitancy \~ treatment + province + treatment \* province

Visualization: Draw the coefficient of treatment \* province on the China map.

```{r}
wtd_lm=lm(vaccine_hesitancy_score ~ province,data=df_video_intervention,weights=weight)
summary(wtd_lm)
```

```{r}
# maps

library(maptools)
library(ggplot2)
library(rgdal)

map_list = data.frame(NAME=c('?ӱ?ʡ','ɽ??ʡ','????ʡ','????ʡ','??????ʡ','????ʡ','?㽭ʡ','????ʡ','????ʡ','????ʡ','ɽ??ʡ','????ʡ','????ʡ','????ʡ','?㶫ʡ','????ʡ','?Ĵ?ʡ','????ʡ','????ʡ','????ʡ','????ʡ','?ຣʡ','???ɹ???????','????׳????????','??????????','???Ļ?????????','?½?ά??????????','??????','?Ϻ???','??????','??????'),resultA=seq(1,31),resultB=seq(1,31),resultC=seq(1,31),resultD=seq(1,31))

for (i in 1:31){
  map_baseline = subset(df_list_baseline,Q5==i,select=c(PartVA_5_T, PartVB_5_T, PartVC_5_T, PartVD_5_T,weight))
  map_treatment = subset(df_list_treatment,Q5==i,select=c(PartVA_5_T, PartVB_5_T, PartVC_5_T, PartVD_5_T,weight))
  result_baseline = c(wtd.mean(map_baseline$PartVA_5_T,map_baseline$weight),wtd.mean(map_baseline$PartVB_5_T,map_baseline$weight),wtd.mean(map_baseline$PartVC_5_T,map_baseline$weight),wtd.mean(map_baseline$PartVD_5_T,map_baseline$weight)) 
  result_treatment = c(wtd.mean(map_treatment$PartVA_5_T,map_treatment$weight),wtd.mean(map_treatment$PartVB_5_T,map_treatment$weight),wtd.mean(map_treatment$PartVC_5_T,map_treatment$weight),wtd.mean(map_treatment$PartVD_5_T,map_treatment$weight)) 
  bs = sum(map_baseline$weight)
  ts = sum(map_treatment$weight)
  result = (ts*result_treatment-bs*result_baseline)/(bs+ts)
  map_list$resultA[i] = result[1]
  map_list$resultB[i] = result[2]
  map_list$resultC[i] = result[3]
  map_list$resultD[i] = result[4]
}

gpclibPermit()

mydat = rgdal::readOGR('bou2_4p.shp')
mysh = fortify(mydat)
mysh = transform(mysh, id = iconv(id, from = 'GBK'), group = iconv(group, from = 'GBK'))
names(mysh)[2:3] = c("x","y")

myepidat = subset(mysh,select = c('id','NAME'))
myepidat = filter(myepidat,!duplicated(myepidat$id))
myepidat$rand = 0

for (i in 1:31){
  myepidat$rand[which(myepidat$NAME == map_list$NAME[i])] = map_list$resultA[i]+map_list$resultB[i]+map_list$resultC[i]+map_list$resultD[i]
}

csmap = ggplot(myepidat) +
    geom_map(aes(map_id = id, fill = rand), color = "white", map = mysh) +
    scale_fill_gradient2(high = "red",mid = "white",low = "#9999FF") +
    expand_limits(mysh) + coord_map()
print(csmap)

```

## Fixed Effect

```{r}
# urban vs. rural
library(nlme)
lme_residence=lme(vaccine_hesitancy_score ~ 1, random = ~1 | residence, data=df_video_intervention)
summary(lme_residence)

# education
lme_education=lme(vaccine_hesitancy_score ~ 1, random = ~1 | education, data=df_video_intervention)
summary(lme_education)

# province
lme_province=lme(vaccine_hesitancy_score ~ 1, random = ~1 | province, data=df_video_intervention)
summary(lme_province)


## linear regression

# age (random:province)
lme_age_pro=lme(vaccine_hesitancy_score ~ Q3A, random = ~1 | province, data=df_video_intervention)
summary(lme_age_pro)

# education (random:province)
lme_edu_pro=lme(vaccine_hesitancy_score ~ Q8, random = ~1 | province, data=df_video_intervention)
summary(lme_edu_pro)

# age + education (random:province)
lme_age_edu_pro=lme(vaccine_hesitancy_score ~ Q3A+Q8, random = ~1 | province, data=df_video_intervention)
summary(lme_age_edu_pro)
```
